\section{Methodology}

The working methodology for this report will be a combination of SysML and UML. With SysML, the non-software parts of the system can be described, e.g. the synthesized mapping onto the hardware or other register-transfer level (RTL) models. UML on the other hand provides a logical and discrete description of software classes or their interaction. As we are modeling a solution based on hardware and software co-design, both methodologies are applicable and will be described in section \ref{sec:archdesign}, architecture and design. The diagrams and models will be derived from a set of requirements put forward in section \ref{sec:req}, requirements. To quickly review the identified diagrams for this report:

\begin{itemize}
	\item Block definition diagram (BDD): To model the overall hardware structure of the system.
	\item Internal block diagram (IBD): To model block-specific inputs and outputs of the algorithm IP block.
	\item Allocation diagram: To show possible hardware allocations of the different blocks shown in the BDD.
	\item State machine diagram: To model the different state of the system, their transitions and guards.
	\item Activity diagram. To show the sequence of actions of the application and which activities it goes through. These are useful to get an overall idea of the use case.
	\item Class diagrams. Depicts the logical software classes, their dependencies and associations.
\end{itemize}

The analysis, design, development and validation phases follow a model-based co-design with UML/SysML inspired by \cite{codesign}. This holistic process takes a starting point in the requirements, derives an architecture and design of the system, then proceeds to an implementation phase where high-level source code is designed, simulated and synthesized to a hardware description language (HDL). It concludes by conducting an entire system validation.
